---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# faviconGeneratoR

<!-- badges: start -->
<!-- badges: end -->

The goal of faviconGeneratoR is to provide some simple wrapper functions to the [realfavicongenerator.net](https://www.realfavicongenerator.net) API. This allows you to create favicons for lots of different platforms from local or online images.

## Installation

Currently, faviconGeneratoR is only available from GitHub. To install, use the `devtools` package:

``` r
# install.packages("devtools")
devtools::install_github("ARawles/faviconGeneratoR")
```
## Example

The main function in the package is `generate_favicon()`. This function uses a number of helper functions to build your request, send it, and save the response:

```{r, eval = FALSE}
convert_to_favicon(image = "www.this.in.an.image.com",
                   save_loc = "C:/Users/me/Downloads",
                   favicon_design = build_favicon_design(ios = ios_helper(),
                                                         windows = windows_helper(),
                                                         firefox_app = firefox_app_helper(),
                                                         android_chrome = android_chrome_helper(),
                                                         safari_pinned_tab = safari_pinned_tab_helper(),
                                                         coast = coast_helper(),
                                                         open_graph = open_graph_helper(),
                                                         yandex_browser = yandex_browser_helper())
)

```

The favicon design can be customised for lots of different platforms. When specifying the properties for each platform, use the `*_helper()` functions to easily provide the required parameters. To exclude a platform, just set the parameter for that platform to `NULL`.
